/-/
title: "Alcohol vs Seat choice"
author: "Jason Briseno"
date: "09/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$ There is no difference in alcohol consumption based on where one sits in class.
$H_H$ There is a  difference in alcohol consumption based on where you sit in class.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  The boxplot shows there is more people that consume alcohol that sit in the back.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

## Inferential Tests
  
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```  
First we got a P value of 0.000116 so we conclude we reject $H_0$; there is a difference in alcohol consumption base on where one sits.



## Conclusions

in conclussion the people in the back consumed more alcohol. there is a slight difference between people who sat in the front from the back, difference from people sitting in the middle from the back and a difference in people sitting from the middle to the front.
